Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-28 fmics/paper.tex
remove lines from table
minor correction to definition of output
make fig 8 tabular too

\usepackage{times,graphicx,epsfig,boxedminipage,url,xspace,array,amsmath}
\newcommand\T{\rule{0pt}{2.6ex}}
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}}

@@

\begin{table}[t]
\caption{
Descriptions of the HOL functions comprising our model of the SRS structure.
\label{tab:descriptions}
}
\begin{tabular}{lp{0.8\textwidth}}
Function&Intended meaning\\
\hline\\
\(\mathsf{tap}\;n\;x\)&The position of tap $x$ of slice $n$.\\
\(\mathsf{input}\;n\)&A pair $(n',x)$ indicating that the input to slice $n$ is output $x$ of slice $n'$.\\
\(\mathsf{delay}\;n\)&The number of time steps between updates of slice $n$.\\
\(\mathsf{source}\;D\;n\;m\;t\)&The value of the cell that is the direct input to cell $m$ of slice $n$, at time $t$, given input stream $D$.\\
\(\mathsf{SR}\;D\;n\;m\;t\)&The value of cell $m$ of shift register $n$, at time $t$, given input stream $D$.\\
\(\mathsf{output}\;D\;n\;x\;t\)&The output at tap $x$ of slice $n$, at time $t$, given input stream $D$.\\
\(\mathsf{RS}\;D\;n\;t\)&The $n$-th running sum at time $t$, given input stream $D$.\\
\(\mathsf{update\_time}\;n\;t\)&A boolean indicating whether $t$ is an update time for slice $n$.
\end{tabular}
\end{table}

@@

\begin{figure}
\caption{
Definitions of the HOL functions comprising our model of the SRS structure.
\(\mathsf{tap}\) and \(\mathsf{input}\) are defined to match Figure~\ref{fig:srs}.
Slice $0$ is a fake slice representing the SRS input; this enables a succinct definition of $\mathsf{source}$.
\vspace{0.2in}
\label{fig:definitions}}
\begin{tabular}{l|ll}
Function \T \B & Definition \\\hline
$\mathsf{tap}\;n\;x$ \T & $\;\mathsf{tap}\;0\;0=0\quad\quad$ & $\mathsf{tap}\;0\;x=0$\\
&$\;\mathsf{tap}\;1\;0=1-1\quad$ &  $\mathsf{tap}\;1\;x=2-1$\\
&$\;\mathsf{tap}\;2\;0=8-1\quad$ &  $\mathsf{tap}\;2\;x=16-1$\\
&$\;\dots\quad$ \B & $\mathsf{tap}\;6\;x=128-1\quad\text{(where each $x>0$)}$\\\hline

$\mathsf{input}\;n$ \T & $\;\mathsf{input}\;0=(0,0)\quad$ & $\mathsf{input}\;1=(0,0)$\\
&$\;\mathsf{input}\;2=(0,0)\quad$ & $\mathsf{input}\;3=(1,1)$\\
&$\;\mathsf{input}\;4=(3,0)\quad$ & $\mathsf{input}\;5=(4,0)$\\
&$\;\mathsf{input}\;6=(4,1)\quad$ \B & $\mathsf{input}\;n=(n-1,0)\quad\text{(where $n>6$)}$\\\hline

$\mathsf{delay}\;n$ \T & $\;\mathsf{delay}\;0=1$\\
&\multicolumn{2}{|l}{$\;\mathsf{delay}\;n=\mathsf{delay}\;n'\times((\mathsf{tap}\;n'\;x)+1)$}\\
&\multicolumn{2}{|l}{$\qquad\qquad\qquad\text{where $(n',x)=\mathsf{input\;n}$ (and $n>0$)}$} \B \\\hline

$\mathsf{source}\;D\;n\;m\;t$ \T & \multicolumn{2}{|l}{\;$\mathsf{source}\;D\;n\;0\;t=\mathsf{output}\;D\;n'\;x\;t\quad\text{where $(n',x)=\mathsf{input\;n}$}$}\\
&\multicolumn{2}{|l}{$\;\mathsf{source}\;D\;n\;m\;t=\;\mathsf{SR}\;D\;n\;(m-1)\;\quad\text{(where $m>0$)}$} \B \\\hline

$\mathsf{SR}\;D\;n\;m\;t$ \T &  \multicolumn{2}{|l}{\;$\mathsf{SR}\;D\;n\;m\;0=0$}\\
&\multicolumn{2}{|l}{$\;\mathsf{SR}\;D\;n\;m\;t=\text{if $\mathsf{update\_time}\;n\;t$}\;\;\;\text{then }$}\\
&&$\mathsf{source}\;D\;n\;m\;(t-1)$\\
&\multicolumn{2}{|l}{$\qquad\qquad\qquad\quad\text{else }\mathsf{SR}\;D\;n\;m\;t\qquad\text{(where $t>0$)}$}\B \\\hline

$\mathsf{output}\;D\;n\;x\;t$ \T &\multicolumn{2}{|l}{$\;\mathsf{output}\;D\;0\;x\;t=D\;t$}\\
&\multicolumn{2}{|l}{$\;\mathsf{output}\;D\;n\;x\;0=0$}\\
&\multicolumn{2}{|l}{$\;\mathsf{output}\;D\;n\;x\;t = \text{if $\mathsf{update\_time}\;n\;t$}\;\;\;\text{then }$}\\
&\multicolumn{2}{|l}{$\qquad\quad((\mathsf{output}\;D\;n\;x\;(t-1))+(\mathsf{source}\;D\;n\;0\;(t-1)))-$}\\
&&$\qquad\qquad\qquad(\mathsf{SR}\;D\;n(\mathsf{tap}\;n\;x)\;(t-1))$\\
&\multicolumn{2}{|l}{$\qquad\qquad\qquad\qquad\text{else }\mathsf{output}\;D\;n\;x\;(t-1)\qquad\text{(where $t>0$)}$}\B\\\hline

$\mathsf{RS}\;D\;n\;t$ \T \B & \multicolumn{2}{|l}{$\;\mathsf{RS}\;D\;n\;t=\mathsf{output}\;D\;\left(\left\lfloor\frac{n}{2}\right\rfloor+1\right)\;(n\operatorname{mod}2)$}\\\hline

$\mathsf{update\_time}\;n\;t$ \T & \multicolumn{2}{|l}{$\;\mathsf{update\_time}\;n\;t\iff(t\operatorname{mod}\mathsf{delay}\;n=0)$}
\end{tabular}
\end{figure}

\begin{figure}
\caption{
Definitions of auxiliary HOL functions used while proving theorems about the model of the SRS structure.
\label{fig:auxdefs}
}
\begin{align*}
\mathsf{delay\_sum}\;0&=0\\
\mathsf{delay\_sum}\;n&=\mathsf{delay}\;n'+\mathsf{delay\_sum}\;n'\\
&\qquad\text{where $(n',\_)=\mathsf{input}\;n$}
\end{align*}
\begin{align*}
\mathsf{last\_update}\;n\;0&=0\\
\mathsf{last\_update}\;n\;t&=\text{if $\mathsf{update\_time}\;n\;t$ then $t$}\\
&\qquad\text{else }\mathsf{last\_update}\;n\;(t-1)\qquad\text{(where $t>0$)}
\end{align*}
\begin{align*}
\mathsf{exact}\;D\;n\;x\;t=\sum_{m=0}^{((\mathsf{tap}\;n\;x)+1)\times(\mathsf{delay}\;n)}\begin{cases}0&t<m+1\\D\;(t-m-1)&\text{otherwise}\end{cases}
\end{align*}
\end{figure}

>>>>

\usepackage{times,graphicx,epsfig,boxedminipage,url,xspace,array,amsmath}

@@

\begin{table}[t]
\caption{
Descriptions of the HOL functions comprising our model of the SRS structure.
\label{tab:descriptions}
}
\begin{tabular}{lp{0.8\textwidth}}
Function&Intended meaning\\
\hline
\(\mathsf{tap}\;n\;x\)&The position of tap $x$ of slice $n$.\\
\(\mathsf{input}\;n\)&A pair $(n',x)$ indicating that the input to slice $n$ is output $x$ of slice $n'$.\\
\(\mathsf{delay}\;n\)&The number of time steps between updates of slice $n$.\\
\(\mathsf{source}\;D\;n\;m\;t\)&The value of the cell that is the direct input to cell $m$ of slice $n$, at time $t$, given input stream $D$.\\
\(\mathsf{SR}\;D\;n\;m\;t\)&The value of cell $m$ of shift register $n$, at time $t$, given input stream $D$.\\
\(\mathsf{output}\;D\;n\;x\;t\)&The output at tap $x$ of slice $n$, at time $t$, given input stream $D$.\\
\(\mathsf{RS}\;D\;n\;t\)&The $n$-th running sum at time $t$, given input stream $D$.\\
\(\mathsf{update\_time}\;n\;t\)&A boolean indicating whether $t$ is an update time for slice $n$.
\end{tabular}
\end{table}

@@

\begin{figure}
\caption{
Definitions of the HOL functions comprising our model of the SRS structure.
\(\mathsf{tap}\) and \(\mathsf{input}\) are defined to match Figure~\ref{fig:srs}.
Slice $0$ is a fake slice representing the SRS input; this enables a succinct definition of $\mathsf{source}$.
\vspace{0.2in}
\label{fig:definitions}}
\begin{tabular}{lll}
Function & Definition\\\hline
$\mathsf{tap}\;n\;x$ & $\;\mathsf{tap}\;0\;0=0\quad\quad$ & $\mathsf{tap}\;0\;x=0$\\
&$\;\mathsf{tap}\;1\;0=1-1\quad$ &  $\mathsf{tap}\;1\;x=2-1$\\
&$\;\mathsf{tap}\;2\;0=8-1\quad$ &  $\mathsf{tap}\;2\;x=16-1$\\
&$\;\dots\quad$ & $\mathsf{tap}\;6\;x=128-1\quad\text{(where each $x>0$)}$\\

$\mathsf{input}\;n$ & $\;\mathsf{input}\;0=(0,0)\quad$ & $\mathsf{input}\;1=(0,0)$\\
&$\;\mathsf{input}\;2=(0,0)\quad$ & $\mathsf{input}\;3=(1,1)$\\
&$\;\mathsf{input}\;4=(3,0)\quad$ & $\mathsf{input}\;5=(4,0)$\\
&$\;\mathsf{input}\;6=(4,1)\quad$ & $\mathsf{input}\;n=(n-1,0)\quad\text{(where $n>6$)}$\\

$\mathsf{delay}\;n$ & $\;\mathsf{delay}\;0=1$\\
&\multicolumn{2}{l}{$\;\mathsf{delay}\;n=\mathsf{delay}\;n'\times((\mathsf{tap}\;n'\;x)+1)$}\\
&\multicolumn{2}{l}{$\qquad\qquad\qquad\text{where $(n',x)=\mathsf{input\;n}$ (and $n>0$)}$}\\

$\mathsf{source}\;D\;n\;m\;t$ & \multicolumn{2}{l}{\;$\mathsf{source}\;D\;n\;0\;t=\mathsf{output}\;D\;n'\;x\;t\quad\text{where $(n',x)=\mathsf{input\;n}$}$}\\
&\multicolumn{2}{l}{$\;\mathsf{source}\;D\;n\;m\;t=\;\mathsf{SR}\;D\;n\;(m-1)\;\quad\text{(where $m>0$)}$}\\

$\mathsf{SR}\;D\;n\;m\;t$ &  \multicolumn{2}{l}{\;$\mathsf{SR}\;D\;n\;m\;0=0$}\\
&\multicolumn{2}{l}{$\;\mathsf{SR}\;D\;n\;m\;t=\text{if $\mathsf{update\_time}\;n\;t$}\;\;\;\text{then }$}\\
&&$\mathsf{source}\;D\;n\;m\;(t-1)$\\
&\multicolumn{2}{l}{$\qquad\qquad\qquad\quad\text{else }\mathsf{SR}\;D\;n\;m\;t\qquad\text{(where $t>0$)}$}\\

$\mathsf{output}\;D\;n\;x\;t$ &\multicolumn{2}{l}{$\;\mathsf{output}\;D\;0\;x\;t=D\;t$}\\
&\multicolumn{2}{l}{$\;\mathsf{output}\;D\;n\;x\;0=0$}\\
&\multicolumn{2}{l}{$\;\mathsf{output}\;D\;n\;x\;t = \text{if $\mathsf{update\_time}\;n\;t$}\;\;\;\text{then }$}\\
&\multicolumn{2}{l}{$\qquad\quad((\mathsf{output}\;D\;n\;x\;(t-1))+(\mathsf{source}\;D\;n\;0\;(t-1)))-$}\\
&&$\qquad\qquad\qquad(\mathsf{SR}\;D\;n(\mathsf{tap}\;n\;x)\;(t-1))$\\
&\multicolumn{2}{l}{$\qquad\qquad\qquad\qquad\text{else }\mathsf{output}\;D\;n\;x\;(t-1)\qquad\text{(where $n,t>0$)}$}\\

$\mathsf{RS}\;D\;n\;t$ & \multicolumn{2}{l}{$\;\mathsf{RS}\;D\;n\;t=\mathsf{output}\;D\;\left(\left\lfloor\frac{n}{2}\right\rfloor+1\right)\;(n\operatorname{mod}2)$}\\

$\mathsf{update\_time}\;n\;t$ & \multicolumn{2}{l}{$\;\mathsf{update\_time}\;n\;t\iff(t\operatorname{mod}\mathsf{delay}\;n=0)$}
\end{tabular}
\end{figure}

\begin{figure}
\caption{
Definitions of auxiliary HOL functions used while proving theorems about the model of the SRS structure.
\label{fig:auxdefs}
}
\begin{tabular}{ll}
Function & Definition\\\hline
$\mathsf{delay\_sum}\;n$
&$\mathsf{delay\_sum}\;0=0$\\
&$\mathsf{delay\_sum}\;n=\mathsf{delay}\;n'+\mathsf{delay\_sum}\;n'$\\
&$\qquad\text{where $(n',\_)=\mathsf{input}\;n$}$\\

$\mathsf{last\_update}\;n$
&$\mathsf{last\_update}\;n\;0=0$\\
&$\mathsf{last\_update}\;n\;t=\text{if $\mathsf{update\_time}\;n\;t$ then $t$}$\\
&$\qquad\text{else }\mathsf{last\_update}\;n\;(t-1)\qquad\text{(where $t>0$)}$\\

$\mathsf{exact}\;D\;n\;x\;t$
&$\mathsf{exact}\;D\;n\;x\;t=\sum_{m=0}^{((\mathsf{tap}\;n\;x)+1)\times(\mathsf{delay}\;n)}\begin{cases}0&t<m+1\\D\;(t-m-1)&\text{otherwise}\end{cases}$
\end{tabular}
\end{figure}
